\documentclass{article}

\usepackage{ctex}

\usepackage{multicol}

\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}

\usepackage{lscape}

\author{Sha Shuang}

\date{April 13,2018}

\title{China¡¯s AI talent strategy: domestic boom, international lure}


\begin{document}


\maketitle



This paper I read mainly tells us about China¡¯s AI talent strategy with the development of AI technology. AI is artificial intelligence that will be the key technology that underpins national power in the future, and the future of AI lies in skilled talents and enormous data. With the rapid rise of AI technology, it is necessary for AI development to be the professional talents, but the talent gap brought resistance. Therefore, AI talent is essential to be the development of the technology.



According to a report released by LinkedIn, of the 1.9 million AI talents in the world, China only accounts for just over 50,000 of them, while the U.S., which tops the rankings, has an AI talent pool of 850,000 individuals. The AI talents occupancy rate of China is very low, and is bad for the AI development. In order to solution this problem, on the one hand, China start carrying out the plan that the New Generation Artificial Intelligence Development Plan, in which it listed accelerating the education of top-notch AI talents as a primary task. For example, Chinese universities have added AI engineering as a new major for their undergraduate students and the number of universities is increasing, and more AI-related coding courses will be set up at the elementary and secondary school levels over the next decade, helping the public better understand AI technologies. On the other hand, China is taking measures to attract tech talents in countries like the U.S. and Finland, and improve the favorable policies to make them work and life comfortable, and encourage more and more returnees to return to China.



In my view, the development of AI technology is now main team, and my major is computer vision and machine leaning in the field of AI. I should make effort to study well this major, and improve myself competitive power, and become a talent in this field, and make a contribution to the development of AI, and realize own value.




\end{document}
