\documentclass{article}

\usepackage{ctex}

\usepackage{multicol}

\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}

\usepackage{lscape}

\author{Shuang Sha}

\date{April 15,2018}

\title{Most of mobile phones on market adapt to China¡¯s Beidou system}


\begin{document}


\maketitle



This paper mainly describe that the field of application for the China-developed positioning system in daily life. One of the field is most of mobile phones on market, adapting to China¡¯s Beidou system. Another of the field is traffic transport. And China¡¯s Ministry of Transport stipulated that all bus tour charters and vehicles carrying hazardous materials should install the Beidou system starting from the beginning of 2013. In addition, each local government in China has incorporated Beidou into their Continuously Operating Reference Stations (CORS). Following of the US¡¯s Global Positioning System (GPS) and Russia's GLONASS, China's BeiDou Navigation Satellite System has become the third recognized positioning system by the United Nations.


China¡¯s beidou Navigation Satellite System is depend on independent research and development by our country¡¯s professional skilled talents, and China has had own positioning system. Beidou Navigation Satellite system is able to provide precise positioning, and can provide tremendous help to the transportation of ocean and land. It is precisely because of the unremitting effort of Chinese scientists, hard struggle and the spirit of space that is the first to take the lead, making that China¡¯s space industry is going up a new level. As a graduate student, I need to make efforts and improve the ability of scientific research, and develop the spirit of space.





\end{document}
